Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-18 ms.qmd
Adding new figure to suppl for temp

#### Exploring the impact of temperature on $lnRR_{Q_{10}}$ PROBABLY JUST MOVE TO THE MAIN TEXT

```{r, lnrrq10_nonlinear}

# Subset the data
lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0 & !is.na(acclim_period)) %>% 
                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE),
                                     max_temp_c = scale(temp_2, scale = FALSE))

rerun = FALSE
if(rerun){
  model1.1_nl <- metafor::rma.mv(effect_size ~ max_temp_c, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

  model1.1_bayes_nl <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  max_temp_c + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c| spp) + (1|trait), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

  # Save model1.1_nl
  saveRDS(model1.1_nl, file = "./output/models/lnRRQ10_1.1_nl")
  saveRDS(model1.1_bayes_nl, file = "./output/models/lnRRQ10_1.1_bayes_nl")
} else{ 
  model1.1_nl <- readRDS("./output/models/lnRRQ10_1.1_nl")
model1.1_bayes_nl <- readRDS("./output/models/lnRRQ10_1.1_bayes_nl")
}

>>>>

#### Exploring the impact of temperature on $lnRR_{Q_{10}}$

```{r, fig-lnrrq10_temp}
#| label: fig-lnrrq10_temp
#| fig-cap: "Bubble plot of the relationship between $lnRR_{Q_{10}}$ and maximum temperature used in treatments within a study. Temperature is centered around the mean temperature in the data."

bubble_plot(model1.2, mod = "max_temp_c", group = "record_num", ylab = TeX("$lnRR_{Q_{10}}"), xlab = TeX("Centered Maximum Temperature ($^{\\circ}$C)"), by = "habitat", condition.nrow = 1)  + theme(axis.title  = element_text(size = 30), 
                        axis.text = element_text(size = 26), 
                        axis.text.y = element_text(size = 26),
                        legend.text = element_text(size = 26), 
                        legend.title = element_text(size = 24))
